---
title: "NVSU ANNUAL ACCOMPLISHMENT REPORT 2022"
subtitle: "ACADEMIC AFFAIRS"
author: IPPRC
format: pdf
editor: visual
execute:
  echo: false
  warning: false
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center')
```

```{r}
library(tidyverse)
```

```{r}
grad <- read_csv("/Users/mildo/OneDrive/Documents/R/NVSU-IPPRC/csv/data1.csv")
grad <- tibble(grad)
```

```{r}
faculty <- read_csv("/Users/mildo/OneDrive/Documents/R/NVSU-IPPRC/csv/data2.csv")
faculty <- tibble(faculty)
faculty <-
  faculty %>%
  mutate_at(vars(Rank), factor)
faculty <- 
  faculty %>%
  mutate(Rank = factor(Rank, levels = c("Instructor", "Assistant Professor",
                                        "Associate Professor", "Professor")))
```

# CURRICULAR PROGRAMS

## Undergraduate/ Graduate Programs



## Center Of Excellence

## Center of Development

# STUDENTS

## Admission Profile

## Enrollment Profile

## Performance in the Licensure  Exam

## Graduation Profile

```{r}
ggplot(data = grad) + 
  geom_point(mapping = aes(x = Campus, y = grad_ss, color = College), position = "jitter") +
  ylab("Number of Graduates") +
  labs(title = "Distribution of Number of Graduates for 2022") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))
```

```{r}
ggplot(grad, aes(x = Campus, y = grad_ss, fill = College)) +
  geom_col(position = "dodge") +
  ylab("Number of Graduates")
```

## Employability of Graduates

## Awards and Recognition

## Scholarships

## Financial Assistance

## Attendance to Seminars, Training, and Workshops

# FACULTY

## Faculty Profile

```{r}
ggplot(faculty) + 
  # dodge rather than stack produces grouped bar plot
  geom_bar(aes(x = College, fill = College)) +
  scale_fill_manual(values = c("yellow", "purple4", "lightgreen", "pink", "darkgreen", "red", "blue", "gray")) +
  ylab(" Number of Faculty")
```

```{r}
ggplot(faculty) + 
  # dodge rather than stack produces grouped bar plot
  geom_bar(aes(x = College, fill = Rank), position = "dodge") +
  ylab("Number of Faculty")
```

## Scholarship/ Development Plan

## Faculty who graduated from pursuing their Advanced Education during the fiscal year

## Attendance/ Participation to Seminars, Training and Workshops

## Graduate Program Faculty Profile

## Engagement in Research

## Awards and Recognition