---
title: "R Notebook"
output: html_notebook
---

```{r}
grad_college <-
  grad %>%
  group_by(College) %>%
  summarise(total_grad = sum(grad_ss),
            .groups = 'drop') %>%
  mutate(percent_grad = round((total_grad/sum(grad$grad_ss))*100,
                              digits = 2))
```

```{r}
#| output: false

ggplot(grad, aes(x = "", y = grad_ss, fill = College)) +
  geom_col(color = "black") +
  geom_text(aes(label = grad_ss),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  scale_fill_brewer() +
  theme_bw() +
  ylab("Bayombong Campus") +
  xlab("")
```

```{r}
#| output: false
ggplot(grad_college, aes(x = "", y = percent_grad, fill = College)) +
  geom_col(color = "black") +
  geom_text(aes(label = percent_grad),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  scale_fill_brewer() +
  theme_void() +
  ylab("Bayombong Campus")
```

```{r}
ggplot(grad, aes(x= College, y= grad_ss, colour="green", label=Name))+
  geom_point() +geom_text(hjust=0, vjust=0)
```

```{r}
ggplot(data = grad) + 
  geom_point(mapping = aes(x = College, y = grad_ss,
                           label = Program)) + geom_text()
```

## Reminders

1. CAS Enrollment don't tally.
2. CTE Enrollment don't tally.
3. data of CBE in enrollment is est.
4. BSBA has enrollment and is not according to semester.
5. Phd graduates in COA, unclear.Placed in PhDA
6. BAS-DVM is also BAS and DVM in graduates.
7. BTVTEd has no graduates and enrollees for CTE Bambang.

## Meeting 031323

### Annual Report 2022

- academic affairs. continue with visualization, and edit. data will be from mr. busa.

- after charter anniversary.

- president wants a draft. the president is a consultant.

### Investiture of the University President

- 

### Charter Anniversary

- 
