---
title: "NVSU ANNUAL ACCOMPLISHMENT REPORT 2022"
subtitle: "ACADEMIC AFFAIRS"
author: IPPRC
format:
  docx:
    toc: true
editor: visual
execute:
  echo: false
  warning: false
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center')
```

# ACADEMIC AFFAIRS

## STUDENTS

### GRADUATES

```{r}
library(tidyverse)
```

```{r}
grad <- read_csv("/Users/mildo/OneDrive/Documents/R/NVSU-IPPRC/csv/data1.csv")
grad <- tibble(grad)
```

```{r}
faculty <- read_csv("/Users/mildo/OneDrive/Documents/R/NVSU-IPPRC/csv/data2.csv")
faculty <- tibble(faculty)
faculty <-
  faculty %>%
  mutate_at(vars(Rank), factor)
faculty <- 
  faculty %>%
  mutate(Rank = factor(Rank, levels = c("Instructor", "Agrad_ssistant Profegrad_ssor",
                                      "Agrad_ssociate Profegrad_ssor", "Profegrad_ssor")))
```

```{r}
ggplot(data = grad) + 
  geom_point(mapping = aes(x = Campus, y = grad_ss, color = College), position = "jitter") +
  ylab("Number of Graduates") +
  labs(title = "Distribution of Number of Graduates for 2022") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))
  
```

### TOTAL

```{r}
ggplot(grad, aes(x = Campus, y = grad_ss, fill = College)) +
  geom_col(position = "dodge") +
  ylab("Number of Graduates")
```

```{r}
grad_college <-
  grad %>%
  group_by(College) %>%
  summarise(total_grad = sum(grad_ss),
            .groups = 'drop') %>%
  mutate(percent_grad = round((total_grad/sum(grad$grad_ss))*100,
                              digits = 2))
```

```{r}
#| output: false

ggplot(grad, aes(x = "", y = grad_ss, fill = College)) +
  geom_col(color = "black") +
  geom_text(aes(label = grad_ss),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  scale_fill_brewer() +
  theme_bw() +
  ylab("Bayombong Campus") +
  xlab("")
```

```{r}
#| output: false
ggplot(grad_college, aes(x = "", y = percent_grad, fill = College)) +
  geom_col(color = "black") +
  geom_text(aes(label = percent_grad),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  scale_fill_brewer() +
  theme_void() +
  ylab("Bayombong Campus")
```

### STUDENT POPULATION

#### TOTAL

### SCHOLARSHIP

#### TOTAL

### STUDENT FINANCIAL Agrad_ssISTANCE RECIPIENTS

### STUDENTS INVOLVED IN INTER-COUNTRY MOBILITY

## FACULTY

```{r}
ggplot(faculty) + 
  # dodge rather than stack produces grouped bar plot
  geom_bar(aes(x = College, fill = College)) +
  scale_fill_manual(values = c("yellow", "purple4", "lightgreen", "pink", "darkgreen", "red", "blue", "gray")) +
  ylab(" Number of Faculty")
```

```{r}
ggplot(faculty) + 
  # dodge rather than stack produces grouped bar plot
  geom_bar(aes(x = College, fill = Rank), position = "dodge") +
  ylab("Number of Faculty")
```

### EMERGENCY INSTRUCTORS

### TOTAL

### 9 ACCREDITED PROFEgrad_ssORS

### 191 RECLAgrad_ssIFIED FACULTY MEMBERS THROUGH NBC 461

### 12 BATCH 1 MERIT PROMOTIONS

### 4 NEW EMPLOYEES THRU SCRAP AND BUILD

### 207 APPOINTEES

## PROGRAMS

### CENTER OF EXCELLENCE

### CENTER OF DEVELOPMENT

### UNDERGRADUATE PROGRAMS

#### WITH ACCREDITATION

#### ACCREDITATION STATUS

## LICENSURE EXAM PERFORMANCE

### FIRST TIME BOARD EXAM PAgrad_ssERS

#### BAYOMBONG

##### AGRICULTURE

##### ENGINEERING

##### FORESTRY

##### TEACHER EDUCATION

##### VETERINARY MEDICINE

#### BAMBANG

##### TEACHER EDUCATION

##### ENGINEERING
