---
title: "NVSU ANNUAL ACCOMPLISHMENT REPORT 2022"
subtitle: "ACADEMIC AFFAIRS"
author: IPPRC
format:
  docx:
    toc: true
editor: visual
execute:
  echo: false
  warning: false
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.align = 'center')
```

# ACADEMIC AFFAIRS

## STUDENTS

### GRADUATES

```{r}
library(tidyverse)
library(labelled)
```

```{r}
no_grad <- read_csv("csv/data2.csv")
no_grad <- tibble(no_grad)
```

```{r}
faculty <- read_csv("csv/data2.csv")
faculty <- tibble(faculty)
faculty <-
  faculty %>%
  mutate_at(vars(Rank), factor)
faculty <- 
  faculty %>%
  mutate(Rank = factor(Rank, levels = c("Instructor", "Assistant Professor",
                                      "Associate Professor", "Professor")))
```

```{r}
var_label(no_grad$ss) <- '2nd Semester'
var_label(no_grad$my) <- 'Mid Year Term'
var_label(no_grad$fs) <- 'First Semester'
```

```{r}
ggplot(data = no_grad) + 
  geom_point(mapping = aes(x = Campus, y = ss, color = College), position = "jitter") +
  ylab("Number of Graduates") +
  labs(title = "Distribution of Number of Graduates for 2022") +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=12,face="bold"))
  
```

### TOTAL

```{r}
lab1 <- aggregate(ss ~ College, no_grad, sum)
ggplot(no_grad, aes(x = Campus, y = ss, fill = College)) +
  geom_col(position = "dodge") +
  ylab("Number of Graduates")

ggplot(faculty) + 
  # dodge rather than stack produces grouped bar plot
  geom_bar(aes(x = College, fill = College)) +
  scale_fill_manual(values = c("yellow", "purple4", "lightgreen", "pink", "darkgreen", "red", "blue", "gray")) +
  ylab(" Number of Faculty")
```

```{r}
no_grad_college <-
  no_grad %>%
  group_by(College) %>%
  summarise(total_grad = sum(ss),
            .groups = 'drop') %>%
  mutate(percent_grad = round((total_grad/sum(no_grad$ss))*100,
                              digits = 2))
```

```{r}
#| output: false

ggplot(no_grad, aes(x = "", y = ss, fill = College)) +
  geom_col(color = "black") +
  geom_text(aes(label = ss),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  scale_fill_brewer() +
  theme_bw() +
  ylab("Bayombong Campus") +
  xlab("")
```

```{r}
#| output: false
ggplot(no_grad_college, aes(x = "", y = percent_grad, fill = College)) +
  geom_col(color = "black") +
  geom_text(aes(label = percent_grad),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  scale_fill_brewer() +
  theme_void() +
  ylab("Bayombong Campus")
```

### STUDENT POPULATION

#### TOTAL

### SCHOLARSHIP

#### TOTAL

### STUDENT FINANCIAL ASSISTANCE RECIPIENTS

### STUDENTS INVOLVED IN INTER-COUNTRY MOBILITY

## FACULTY

```{r}
ggplot(faculty) + 
  # dodge rather than stack produces grouped bar plot
  geom_bar(aes(x = College, fill = College)) +
  scale_fill_manual(values = c("yellow", "purple4", "lightgreen", "pink", "darkgreen", "red", "blue", "gray")) +
  ylab(" Number of Faculty")
```

```{r}
ggplot(faculty) + 
  # dodge rather than stack produces grouped bar plot
  geom_bar(aes(x = College, fill = Rank), position = "dodge") +
  ylab("Number of Faculty")
```

### EMERGENCY INSTRUCTORS

### TOTAL

### 9 ACCREDITED PROFESSORS

### 191 RECLASSIFIED FACULTY MEMBERS THROUGH NBC 461

### 12 BATCH 1 MERIT PROMOTIONS

### 4 NEW EMPLOYEES THRU SCRAP AND BUILD

### 207 APPOINTEES

## PROGRAMS

### CENTER OF EXCELLENCE

### CENTER OF DEVELOPMENT

### UNDERGRADUATE PROGRAMS

#### WITH ACCREDITATION

#### ACCREDITATION STATUS

## LICENSURE EXAM PERFORMANCE

### FIRST TIME BOARD EXAM PASSERS

#### BAYOMBONG

##### AGRICULTURE

##### ENGINEERING

##### FORESTRY

##### TEACHER EDUCATION

##### VETERINARY MEDICINE

#### BAMBANG

##### TEACHER EDUCATION

##### ENGINEERING
